Visualizations for the manuscript

### 2022-05-19 metanalysis_visualization/manuscript_Figures.Rmd
adding total number of encounters and IQR calculations

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales", "EHRtemporalVariability", "plotly", "gmodels", "flextable")
paket(listOfPackages)

@@

@@

```{r}
median_table1_all <- length_hospitalisation_values_all %>% 
  group_by(period) %>% 
  summarise(median_hospitalisation = median(len_hospitalisation)) %>% 
  pivot_wider(names_from = period, values_from = median_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "median") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
median_table1_all$before_pandemic_count <- as.character(median_table1_all$before_pandemic_count)
median_table1_all$during_pandemic_count <- as.character(median_table1_all$during_pandemic_count)

@@

```{r}
bootstrap_pvalue_calculation <- function(df, ...) {
  z <- unique(df[["observed_slope_coefficient"]]) / sd(df[["bootstrapped_slope_coefficient"]])
  pvalue_coeff_interaction <- round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  pvalue_coeff_interaction <- ifelse( pvalue_coeff_interaction >= 0.01, round( pvalue_coeff_interaction, 2), pvalue_coeff_interaction)
  data.frame("pvalue" = pvalue_coeff_interaction,
       "observed_slope_coefficient" = round(unique(df[["observed_slope_coefficient"]]), 2)
  )
}
```

@@

```{r bootstrap_plot}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.02) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

>>>>

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("plotly", "tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales", "EHRtemporalVariability", "gmodels", "flextable", "data.table")
paket(listOfPackages)

@@

```{r}
total_unique_encounters <- patient_count_psy_period_psy_all %>% 
  group_by(period) %>% 
  summarise(total_unique_encounters = sum(count_no_psy_patients + count_psy_patients))
```

@@

```{r}
median_table1_all <- length_hospitalisation_values_all %>% 
  group_by(period) %>% 
  summarise(median_hospitalisation = paste0(median(len_hospitalisation), " (", IQR(len_hospitalisation), ")")) %>% 
  pivot_wider(names_from = period, values_from = median_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "median") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
median_table1_all$before_pandemic_count <- as.character(median_table1_all$before_pandemic_count)
median_table1_all$during_pandemic_count <- as.character(median_table1_all$during_pandemic_count)

@@

```{r}
bootstrap_pvalue_calculation <- function(df, ...) {
  z <- unique(df[["observed_slope_coefficient"]]) / sd(df[["bootstrapped_slope_coefficient"]])
  pvalue_coeff_interaction <- round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  pvalue_coeff_interaction <- ifelse( pvalue_coeff_interaction >= 0.01, round( pvalue_coeff_interaction, 2), pvalue_coeff_interaction)
  data.frame(
    "pvalue" = pvalue_coeff_interaction,
    "observed_slope_coefficient" = round(unique(df[["observed_slope_coefficient"]]), 2)
  )
}
```

@@

```{r bootstrap_plot}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.005) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))
